\section{Installation Instructions}
Below is the install instructions for the server application and Puddle.

\subsection{Hardcoded Information}
It should be noted, that the IP, port and name of the database is hardcoded into the constructor for the \ac{api} class in the serverside code. In Puddle the IP address, name of the central database, username and password for the central database, as well as insertion of information when pressing the Insert button is hardcoded. For Puddle are hardcoded information is found in the \lstinline|MainActivity|.

\subsection{Prerequisites for the server application installation}
The system running the serverside application is expected to run on a Linux system with MySQL installed.

\begin{itemize}
\item MySQL Connector/C
\begin{itemize}
	\item Download from \cite{mysqlconnector}
	\item Place headers in usr/local/include
	\item Place libs (libmysql.so etc) in usr/local/lib
\end{itemize}
\item JsonCPP
\begin{itemize}
	\item Install instructions found at \citep{jsoncppinstall}
	\item Place headers in usr/local/include
	\item Place libs (renamed to libjson.so, libjson.a) in usr/local/include
\end{itemize}
\item Add line /usr/local/lib to etc/ld.so.conf and run \lstinline|sudo ldconfig|
\item Unit tests require BOOST to be installed.\citep{boostinstall}
\end{itemize}

\subsection{Building the Program}
\begin{itemize}
\item Download the code from \citep{install}.
\item In the terminal cd to \lstinline|source/server|
\item run \lstinline|make all|
\item run \lstinline|./serverapp|
\end{itemize}
The server is now running. Type \lstinline|stop| to exit.

\subsection{Running Unit Tests}
\begin{itemize}
\item In the terminal cd to \lstinline|source/server|
\item run \lstinline|make test|
\item run \lstinline|./test_connection|, \lstinline|./test_database| or 
\lstinline|./test_api|.
\end{itemize}
The database unit test requires a database called \lstinline|giraf| accessible by user \lstinline|giraf@localhost| identified by \lstinline|123456|.

Connection unit test requires permission to open listening sockets and requires TCP ports \lstinline|1238| and \lstinline|1239| to be free.

\subsection{Prerequisites for the Puddle Android application}
\begin{itemize}
\item Android SDK.
\item Development IDE. Eclipse has been used, but IntelliJ IDEA and Android Studio should work.
\item Java Development Kit.
\item Connector/J library. Included in the library folder of the project. Can also be downloaded from \citep{mysqlconnectorj}.
\end{itemize}

\subsection{Building Puddle Android Application}
Import the project into your IDE, and build it. Importing in Eclipse can be done by pressing File -> Import -> Existing Projects into Workspace -> Select root directory and navigate to the Puddle folder.

\subsection{Running the Puddle Android Application}
Puddle requires Android version 3.0 or higher to run.

\subsection{License}
The report content is freely available, but publication (with source), only with credit to the authors.

GIRAF Database's source code is released under the GPLv3 \cite{GNUlicense} open source license. This means that you are free to inspect the source code at any time or contribute to the project yourself.

\subsection*{Online Availability} The installation guide and the latest, commented version of the code can also be found online \cite{install}.