\section{Sprint 1 (Week 10 \& 11)}
For this sprint our goal was to create a connection library, a database library, a method of authentication and a database schema.

\textbf{Connection Library} - The connection library is able to receive and send requests between two different computers. We have also written unit tests for this task. The connection library is finished and should compile on Linux.

\textbf{Database Library} - The basic database library functionality has been completed, and unit tests have been written for this functionality.

\textbf{Authentication} - Authentication has been pushed to a later sprint as neither we or the admin group had time to look it over.

\textbf{Database Schema} - We have designed a database schema with attributes. It is mostly done, but might have to be extended depending on what features are needed.


\section{Sprint 2 (Week 12 \& 13)}
The goals for this sprint was to design a database API, set up basic communication between this project and the admin group, and to make a problem statement.

This sprint was very short due to a lot of courses and Easter holidays. Because of this, we started to design the database API and wrote a problem statement. Communication has been delayed to a later sprint.

\section{Sprint 3 (Week 14, 15 \& 16)}
Goals for this sprint include creating a JSON encoder and decoder, creating an OasisLib dummy, making the database build script and creating API-calls for all reads.

\textbf{JSON encoder/decoder} - The JsonCPP library was chosen for this task. It will make it possible for us to receive JSON API-calls and translate them to the C++ that we are using for the database.

\textbf{OasisLib dummy} - Will make it possible for other groups to bypass the local database (which as of now cannot communicate with the central database), and connect directly to the live central database when making calls to the local database. The idea is that when a local database is functional, other groups can make use of it without changing their programs.

During this sprint JSON encoder/decoder, OasisLib dummy and database build script were finished. The API-calls, however, were delayed to sprint 4.

\section{Sprint 4 (Week 17 \& 18)}
The goal for this sprint was to finish the API-calls in order to complete the work on the central database. And to set up communication with the Admin group. Work on synchronization was started.

Most of the API-calls were not completed in the previous sprint. Apart from some of the read-calls, all the calls still needed to be implemented and tested. 

We managed to implement and unit test most of the calls. There were some complications with the Admin group, they crashed the server due to a bug in the code. The synchronization was not done at the end of this sprint, so that and the rest of the calls was postponed to sprint 5.  

\section{Sprint 5 (Week 19)}
This sprint was intended for debug. We implemented the last API calls and tested them, and got the server running after the crash mentioned in sprint 4. We also encouraged the Admin group to build a local version of our server to ensure that they could continue working if the server crashed.

We finished one-way synchronization between the databases, but work on the testing and the two-way synchronization spilled over into the next sprint.

\section{Sprint 6 (Week 20, 21 \& 22)}
The goal for final sprint of the semester was to complete the documentation of the work we had done in the form of a report and to finish up the synchronization.

Some of the documentation was written as we went along but most of the report was still not done. 

In this sprint we managed to complete the documentation and proofread the report and we implemented the final version of our basic two-way synchronization.

